Ecuador plant species TRY data

### 2022-10-31 code/L0/L0_Ecuador_plants_TRY.Rmd
add summary information using mde, DataExplorer, and summarytools packages summarytools summary is giving error

# Load required packages
```{r}
library(rtry)
```

@@

>>>>

# Load required packages
```{r}
library(rtry)
library(mde)
library(DataExplorer)
library(summarytools)
```

@@

# Summary of data
```{r}
summary(data)
na_summary(data, , exclude_cols = c("RelUncertaintyPercent", "V28"))
```

### using DataExplorer package
```{r}
plot_str(data)
introduce(data)
plot_intro(data)
plot_missing(data)
plot_bar(data)
```

### using summarytools package
```{r}
ecuador_TRY_plant_traits_summary <- dfSummary(data, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(ecuador_TRY_plant_traits_summary, method = "render")
view(ecuador_TRY_plant_traits_summary, file = file.path(output_path,"ecuador_TRY_plant_traits_summary.html"))
# gives the following error: Error in withCallingHandlers(expr, warning = function(w) if (inherits(w, : 
#   invalid multibyte string at '<b0>45''
```

# Write data to csv
```{r}
ecuador_TRY_plant_traits_path <- file.path(output_path,"Ecuador_TRY_plant_traits.csv")
write.csv(data, file = ecuador_TRY_plant_traits_path)

```
